Baseline centering problem

### 2019-01-12 paper/tangotd.tex

>>>>

What I don't like here: This still does not capture the composition of
policies/goals (like: to go to $s_2$, first go to $s_1$ via the
$s_1$-policy, then apply the known $s_2$-policy from $s_1$). The
Newton--Bellman equation captures, \emph{for a fixed policy}, the
composition of paths of that policy. But the above still treats
$z(s_1,s_2;\omega)$ as a separate problem for each $\omega$.
